### 2016-09-27 revision/conclusions.tex
Fix conclusions section

We have designed two scale-free algorithms based on \textsc{Follow The
Regularizer Leader}.  Their regret is $O \left(\sqrt{\sup_{v \in K} f(v)
\sum_{t=1}^T \|\ell\|_*^2} \right)$ where $f$ is any non-negative $1$-strongly
convex function with respect to a norm $\|\cdot\|$ defined on the decision set
and where $\|\cdot\|_*$ is the dual norm to $\|\cdot\|$.

A similar, but weaker result holds for a scale-free algorithm based on
\textsc{Mirror Descent}. However, we have also shown this algorithm to be strictly
weaker than algorithms based on \textsc{Follow The Regularizer Leader}. Namely,
we gave examples of regularizers for which the scale-free version of
\textsc{Mirror Descent} has $\Omega(T)$ regret or worse.

@@

We have shown that the scale-free \textsc{FTRL}-based algorithm \textsc{SOLO FTRL} has
regret $O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} + \max_{t=1,2,\dots,T}
\|\ell_t\|_* \sqrt{T} \right)$ with respect to any competitor $u \in K$, where
$f$ is any non-negative $1$-strongly convex function defined on the decision
set.  The latter result makes sense even when the decision set $K$ is
unbounded. Notice that with the regularizer $f(u) = \frac{1}{2}\|u\|_2^2$ the
regret depends quadratically on the norm of the competitor $\|u\|_2$. There
exist non-scale-free algorithms \cite{McMahan-Streeter-2012,
McMahan-Abernethy-2013, Orabona-2013, McMahan-Orabona-2014, Orabona-2014} that
have only a $O(\|u\|_2 \sqrt{\log \|u\|_2})$ or $O(\|u\|_2 \log \|u\|_2)$
dependency.  These algorithms assume an a priori bound on the norm of the loss
vectors.  This leads to another open problem:
%
\begin{quotation}
\noindent
\emph{Is there a scale-free algorithm for the decision set $\R^d$, the regret of
which has $O(\|u\|_2 \sqrt{\log \|u\|_2})$ dependency on the competitor $u$?}
\end{quotation}

>>>>

We have designed a scale-free algorithm based on \textsc{Follow The Regularizer
Leader}. Its regret is $O \left(f(u) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} +
\min{\sqrt{T}, D} \max_{t=1,2,\dots,T} \|\ell_t\|_* \right)$ with respect to any
competitor $u \in K$, where $f$ is any non-negative $1$-strongly convex function
defined on $K$ and $D$ is the diameter of $K$. The result makes sense even when
the decision set $K$ is unbounded.

A similar, but weaker result holds for a scale-free algorithm based on
\textsc{Mirror Descent}. However, we have also shown that this algorithm is
strictly weaker than algorithms based on \textsc{Follow The Regularizer Leader}.
Namely, we gave examples of regularizers for which the scale-free version of
\textsc{Mirror Descent} has $\Omega(T)$ regret or worse.

@@

Notice that with the regularizer $f(u) = \frac{1}{2}\|u\|_2^2$ the regret of
\textsc{SOLO FTRL} depends quadratically on the norm of the competitor
$\|u\|_2$. There exist non-scale-free algorithms \cite{McMahan-Streeter-2012,
McMahan-Abernethy-2013, Orabona-2013, McMahan-Orabona-2014, Orabona-2014} that
have only a $O(\|u\|_2 \sqrt{\log \|u\|_2})$ or $O(\|u\|_2 \log \|u\|_2)$
dependency.  These algorithms assume an a priori bound on the norm of the loss
vectors. It remains an open problem to design algorithms that have sub-quadratic
dependency on $\norm{u}_2$ and are adaptive to the scale of the loss vectors.

### 2016-09-27 revision/introduction.tex
Fix conclusions section

Our proof techniques rely on new homogeneous
inequalities (Lemmas~\ref{lemma:recurrence-solution}, \ref{lemma:useful})
which might be of independent interest.

>>>>

Our proof techniques rely on new homogeneous
inequalities (Lemmas~\ref{lemma:useful}, \ref{lemma:recurrence-solution})
which might be of independent interest.

### 2016-09-27 revision/mirror-descent.tex
Fix conclusions section

Per-coordinate version of \textsc{Scale-Free MD} with regularizer $R(w) =
\frac{1}{2}\norm{w}_2^2$ is exactly the same as the diagonal version of
\textsc{AdaGrad MD}~\cite{Duchi-Hazan-Singer-2011}.

@@

The first counter-example is stated as
Theorem~\ref{theorem:first-counter-example} below; our proof is
in~\ref{section:mirror-descent-proofs}. The decision set is the whole space
$K=V$ and the regularizer is $R(w) = \frac{1}{2}\|w\|_2^2$. Note that $R(w)$ is
$1$-strongly convex with respect to $\|\cdot\|_2$ and the dual norm of
$\|\cdot\|_2$ is $\|\cdot\|_2$. The corresponding Bregman divergence is
$\Breg_R(u,v) = \frac{1}{2}\|u-v\|_2^2$. The counter-example constructs a
sequence of unit-norm loss vectors in the one-dimensional subspace spanned by
the first vector of the standard orthnormal basis.  On such a sequence,
\textsc{GIGA} and both versions of \textsc{AdaGrad MD} have predictions
identical to \textsc{Scale-Free MD}. Hence the lower bound applies to all four
algorithms.

>>>>

Per-coordinate version of \textsc{Scale-Free MD} with regularizer $R(w) =
\frac{1}{2}\norm{w}_2^2$ is exactly the same algorithm as the diagonal version
of \textsc{AdaGrad MD}~\cite{Duchi-Hazan-Singer-2011}.

@@

The first counter-example is stated as
Theorem~\ref{theorem:first-counter-example} below; our proof is
in~\ref{section:mirror-descent-proofs}. The decision set is the whole space
$K=V$ and the regularizer is $R(w) = \frac{1}{2}\|w\|_2^2$. Note that $R(w)$ is
$1$-strongly convex with respect to $\|\cdot\|_2$ and the dual norm of
$\|\cdot\|_2$ is $\|\cdot\|_2$. The corresponding Bregman divergence is
$\Breg_R(u,v) = \frac{1}{2}\|u-v\|_2^2$. The counter-example constructs a
sequence of unit-norm loss vectors in the one-dimensional subspace spanned by
the first vector of the standard orthnormal basis.  On such a sequence, both
versions of \textsc{AdaGrad MD} as well as  \textsc{Scale-Free MD} are identical
to gradient descent with step size $1/\sqrt{t}$, i.e., they are identical
Zinkevich's \textsc{Generalized Infinitesimal Gradient Ascent} (\textsc{GIGA})
algorithm~\cite{Zinkevich-2003}. Hence the lower bound applies to all these
algorithms.
